
%-------------------------
% CV: Jose Nino
%------------------------

%-------------------------
% Sources:
%   Resume in Latex
%     Author : Aras Gungore
%     License : MIT
%   [University of Pennsylvania](https://cdn.uconnectlabs.com/wp-content/uploads/sites/74/2019/08/CV-economics-sample.pdf)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome5}
\usepackage{wasysym}
\usepackage{changepage} % adjust margin for part of text
\input{glyphtounicode}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\Item}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\smallbullet}{\,\begin{picture}(-1,1)(-1,-3)\circle*{3}\end{picture}\ }


\newcommand{\Subheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, #2 & #3 \\
      \small#4 \\
    \end{tabular*}\\
}


\newcommand{\SubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}
}

\newcommand{\HeaderItems}[6]{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l}
      #1 & #3 \\
      #2 & #4 \\
      #5 & #6 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\EducationHeading}[7]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      % School, location, graduation date
      \textbf{#1,} #2 & #3 \\
      % Degree, GPA
      {\small#4} \vspace{5pt} \\
      % Thesis title
      \textit{\small\href{#6}{#5}}\vspace{-7pt}
    \end{tabular*}
    % Thesis abstract
    \begin{itemize}
      \item \small#7
    \end{itemize}
}


\newcommand{\ProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\OrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\SubItem}[1]{\Item{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\SubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\SubHeadingListEnd}{\end{itemize}}
\newcommand{\ItemListStart}{\begin{itemize}}
\newcommand{\ItemListEnd}{\end{itemize}}

\newcommand{\ProjectTitle}[1]{\textit{\small #1} \vspace{-7pt}}
\newcommand{\ProjectDescription}[1]{\vspace{3.5pt} \begin{adjustwidth}{7pt}{0pt} \small#1 \end{adjustwidth}}

\newcommand{\PaperTitle}[1]{\item \textbf{#1} \vspace{-7pt} }
\newcommand{\PaperTitleLinks}[2]{\item \textbf{#1} $|$ #2 \vspace{-7pt} }
\newcommand{\PaperTitleAuthor}[2]{\item \noindent \textbf{#1} #2 }



%-------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge Jose Nino} \\
\end{center}

\HeaderItems
  { \hspace{-4.4pt} {\large \phone} \href{tel:6412606902}{(641) 260-2602} }
  { \faEnvelope \hspace{1pt} \href{mailto:j.nino506@gmail.com}{j.nino506@gmail.com} }
  { \hspace{-4.2pt}\hspace{1pt} \faLinkedin \hspace{-1.2pt}\hspace{3pt} \href{https://www.linkedin.com/in/cheyennequijano}{linkedin.com/in/cheyennequijano} }
  { \faGithub \hspace{1pt} \href{https://github.com/cheyennequijano}{github.com/cheyennequijano} }
  { \hspace{-3pt}\hspace{1pt} {\small \faMapMarker} \hspace{-1.8pt}\hspace{1pt} \href{https://www.google.com/maps/place/Board+of+Governors+of+the+Federal+Reserve+System/@38.8936667,-77.0460803,18.65z/data=!4m6!3m5!1s0x89b7b7a5ff607921:0xcb9fc5f71f1038f9!8m2!3d38.8933102!4d-77.0458087!16s\%2Fg\%2F1tjyvhcj?entry=ttu}{Washington, D.C.} }
  { {\small \faLink} \href{https://www.cheyennequijano.com}{www.cheyennequijano.com} }



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \SubHeadingListStart
    
    \EducationHeading
    {Duke University} {Durham, North Carolina}{Aug 2018 \textbf{-} May 2022}
    {Bachelor of Science with Distinction in Economics, Minor in Mathematics} 
    {Honors Thesis: ``A Perfect Storm: The Effect of Natural Disasters on Child 
      Health''}{https://dukespace.lib.duke.edu/dspace/handle/10161/25559}
    {Advised by Erica Field and Michelle Connolly, I examine the effects of 
    flooding on diarrhea and acute respiratory infection after Typhoon Labuyo 
    in the Philippines. Using ArcGIS and NASA satellite data, I identified each 
    household's distance from the nearest flooded area. I constructed a spatial 
    regression discontinuity design, comparing children exposed to flooding to 
    children living just outside the flood border. My research contributed a 
    novel flooding measure, as previous studies relied on government reports.}

  \SubHeadingListEnd



%----------- RELEVANT COURSEWORK & SKILLS -----------

\section{Relevant Coursework and Skills}
  \vspace{2pt}
  \SubHeadingListStart
    \small{\item{
        \textbf{Economics: }{Econometrics and Data Science, Economics of Global 
            Health, Labor and Family Economics, Intermediate Microeconomics, 
            Intermediate Macroeconomics, Economics of Entrepreneurship, Global 
            Domestic Policy}
            
        \textbf{Mathematics: }{Real Analysis, Mathematical Statistics, Ordinary 
          and Partial Differential Equations, Linear Algebra and Differential 
          Equations, Probability, Multivariable Calculus}

        \textbf{Computer Science: }{Data Structures and Algorithms, 
          Introduction to Computer Science}

        \textbf{Programming Languages: }{Python, R, Stata, HTML, CSS, 
          JavaScript, Java, Julia, MATLAB}
    }}
  \SubHeadingListEnd



%----------- RESEARCH INTERESTS -----------

  \section{Research Interests}
  \vspace{3pt}
  \SubHeadingListStart
  
  \small{\item{
      Development Economics, Economics of Crime, Economics of Corruption, and 
      Economic Development
  }}

  \SubHeadingListEnd



%----------- PROJECTS -----------

\section{Works in Progress}
    \vspace{3pt}
    \SubHeadingListStart
      
      \PaperTitleLinks{``The Effect of Deportations on Crime''}{\href{https://github.com/cheyennequijano/deportations-crime}{\color{blue}GitHub}}
        \ItemListStart
          \Item{I propose that the little evidence of 
            any reduction in crime in response to deportation policies stems 
            from heterogeneous effects on various crime types. My plan involves 
            conducting an event study to examine different responses of crime 
            types over time following the enactment and dissolution of the 
            Secure Communities program in the U.S. The empirical results will 
            serve as a foundation for developing an extended labor market 
            search and matching model incorporating Becker's (1974) model of 
            crime to identify any changes in legal and criminal employment 
            following the policy.}
        \ItemListEnd
      \PaperTitleAuthor{``The Role of Industrial Policy: Evidence from China's Semiconductor Industry''}
        {with Colin Caines (Federal Reserve), Sharon Jeon (Federal Reserve), 
        and Eva Van Leemput (Federal Reserve)}
      \PaperTitleAuthor{``Limitations of the Income Pooling Hypothesis''}
        {with \'{A}ngel Garc\'{i}a-Lascurain Fern\'{a}ndez (Arizona State 
        University), Marjorie McElroy (Duke University), and Ziyuan Wang 
        (University of British Columbia)}

    \SubHeadingListEnd



%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \SubHeadingListStart

    \Subheading
      {Federal Reserve Board of Governors}{Washington, District of Columbia}{Jul 2022 \textbf{-} Present}
      {Research Assistant}
      \ProjectTitle{Illegal Commodities and the Business Cycle}
        \ItemListStart
          \Item{The Illegal Commodities and the Business Cycle project 
            investigates the effects of legal and illegal commodity (cocaine) 
            price changes on the business cycle in Latin America. Under 
            Mar\'{i}a Aristiz\'{a}bal-Ram\'{i}rez, I coded cumulative 
            orthogonal IRFs in Stata and sourced domestic activity data for the 
            studied countries. This involved extensive searches across various 
            sources, including current literature and official websites in 
            Spanish. To ensure comprehensive data coverage, I explored 
            alternate sources, such as using employee and wage data to 
            construct average wages.}
        \ItemListEnd

      \vspace{0.4cm}

      \ProjectTitle{The Impact of China's Demographic Cliff on Outward Investments}
        \ItemListStart
          \Item{The Impact of China's Demographic Cliff on Outward Investments 
            project quantifies the impact of demographic changes on growth in 
            China. Under Colin Caines, Fran\c{c}ois de Soyres, and \'{E}tienne 
            Gagnon, I primarily implement the overlapping generations model 
            code in Julia. By conducting thorough searches on the Chinese 
            statistical agency's websites, I sourced crucial data that had not 
            been used in the existing literature. I also contributed to 
            discussions on refining the China OLG model, deciding on features 
            to retain from the U.S. model and new incorporations.}
        \ItemListEnd

      \ProjectTitle{The Role of Industrial Policy: Evidence from China's Semiconductor Industry}
        \ItemListStart
          \Item{The Role of Industrial Policy Planning project assesses the 
            impact of industrial policy on economic growth and future 
            innovation, focusing on China's semiconductor industry. My primary 
            responsibilities involve cleaning large datasets, crafting charts 
            to highlight relevant stylized facts, and contributing to the 
            writing process with Colin Caines and Eva Van Leemput. I play a key 
            role in organizing ideas, identifying crucial charts and results, 
            and, during the drafting and refining stages, suggesting potential 
            new data sources and ways to enhance our data presentation for a 
            more robust analysis. }
        \ItemListEnd
    
    \Subheading
    {DevLab}{Durham, North Carolina}{Aug 2021 \textbf{-} May 2022}
    {Research Assistant}
      \ProjectTitle{COVID-19 and Household Well-Being in Developing Countries}
      \ItemListStart
        \Item{The COVID-19 and Household Well-Being in Developing Countries 
          project investigates corruption in the trade of essential medical 
          supplies during the COVID-19 pandemic. Under Erica Field and Erik 
          Wibbels, I used Python to apply methods from the illicit financial 
          flows literature to quantify and visualize price gaps in import and 
          export data across Comtrade country transactions. By identifying 
          significant price disparities across transit countries, my results 
          directed us to explore the drivers behind why these countries were 
          particularly corrupt in medical supplies. }
      \ItemListEnd

    \vspace{-14pt}

    \Subheading
    {Environmental Justice Lab}{Durham, North Carolina}{May 2021 \textbf{-} May 2022}
    {Research Assistant}
      \ProjectTitle{Residential Location and Segregation}
      \ItemListStart
        \Item{The Residential Location and Segregation project assesses racial 
          discrimination in the U.K. housing market. Under Christopher Timmins 
          and Amy Binner, I collaborated with other research assistants to 
          design, test, and deploy a program that scrapes rental listings and 
          sends inquiries to realtors from different racial backgrounds. I 
          integrated economic design into the project by addressing a potential 
          endogeneity issue in random assignment and implementing improvements. 
          I also included a crucial tracking feature that aided data recovery, 
          restoring over 300 observations for analysis. }
      \ItemListEnd
    
      \Subheading
    {McElroy Labor Lab}{Durham, North Carolina}{Feb 2021 \textbf{-} May 2022}
    {Research Assistant}
    \ProjectTitle{Limitations of the Income Pooling Hypothesis}
      \ItemListStart
        \Item{The Limitations of the Income Pooling Hypothesis project argues 
          that the hypothesis falls short, citing inconclusive results across 
          theoretical labor economics papers. I identified the models' 
          hypothesis tests and results, contributed to discussions, and crafted 
          a narrative around the findings. }
      \ItemListEnd
    \ProjectTitle{Joint Determination of Labor and Marriage Market Outcomes}
      \ItemListStart
        \Item{The Joint Determination of Labor and Marriage Market Outcomes 
          project proposes that the labor and marriage markets are jointly 
          determined. I constructed instruments for the marriage market 
          equations and coded the 3SLS, 2SLS, reduced form, and OLS estimates 
          for the model in Stata.}
      \ItemListEnd

  \SubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
\vspace{2pt}
\SubHeadingListStart
  \small{\item{
      \textbf{Horey Family Scholarship: }{Awarded to promising undergraduate 
        women in economics.}

      \textbf{Women's Impact Network Scholarship: }{Awarded to undergraduate 
        women who demonstrate leadership qualities.}
  
      \textbf{Facebook Above \& Beyond Computer Science Program: }{Selected 
        to participate in a 10-week coding workshop series with Facebook 
        engineers.}
  }}
\SubHeadingListEnd



%----------- TEACHING EXPERIENCE  -----------

\section{Teaching Experience}
  \SubHeadingListStart
    
    \Subheading
    {Research Assistant Technical Training}{Washington, District of Columbia}{Jun 2023 \textbf{-} Sep 2023}
    {Lecturer and Teaching Assistant}
      \vspace{-10pt}
      \ItemListStart
        \Item{I taught 8 lectures on various programming languages to 
        new research assistants at the Federal Reserve, revised existing 
        materials for clarity, and designed new coding exercises to reinforce 
        comprehension.}
      \ItemListEnd
  
  \SubHeadingListEnd



%----------- ADDITIONAL ACTIVITIES  -----------

\section{Additional Activities}
  \SubHeadingListStart
    
    \Subheading
    {Federal Reserve Education Outreach (FedEd)}{Washington, District of 
    Columbia}{Jan 2023 \textbf{-} Present}
    {Leadership Team Member}
      \vspace{-10pt}
      \ItemListStart
        \Item{FedEd is a research assistant-led program that provides high 
          school students from underrepresented backgrounds exposure to 
          economics through school presentations on various topics. I revise 
          existing materials for better understanding and devise new lectures 
          on current research. Additionally, I am organizing a speaker series 
          at the Federal Reserve that features a presentation on how to think 
          like an economist, a fireside chat with division directors, and a 
          Q\&A session where research assistants will share insights from their 
          career journeys in economics.}
      \ItemListEnd

    \SubHeadingListEnd



%----------- HOBBIES -----------

\section{Hobbies}
  \SubHeadingListStart
    \small{\item{Running (Half-Marathon, Sprint Triathlon), Figure Skating, 
      Taekwondo, A Capella}}
  \SubHeadingListEnd



%----------- REFERENCES -----------

\section{References}

  \SubHeadingListStart
    \item{
      Dr. Christopher Timmins \\
      Gary J. Gorman Affordable Housing Professor \\
      The Wisconsin School of Business \\
      Email: \href{mailto:ctimmins@wisc.edu}{ctimmins@wisc.edu} \\
    }
    \item{
      Dr. Erica Field \\
      Professor of Economics \\
      Duke University \\
      Email: \href{mailto:emf23@duke.edu}{emf23@duke.edu} \\
    }
    \item{
      Dr. Eva Van Leemput \\
      Chief \\
      Federal Reserve Board of Governors \\
      Email: \href{mailto:eva.vanleemput@frb.gov}{eva.vanleemput@frb.gov} \\
    }
    \item{
      Dr. Mar\'{i}a Aristiz\'{a}bal-Ramirez \\
      Economist \\
      Federal Reserve Board of Governors \\
      Email: \href{mailto:maria.aristizabalramirez@frb.gov}{maria.aristizabalramirez@frb.gov} \\
    }
  \SubHeadingListEnd



%-------------------------------------------

\end{document}
